Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-04-25 doc/paper.tex
updates results

\begin{table*}[t!]
    \centering
    \resizebox{0.6\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\% & 10\% & 20\% & 30\% & 40\% & 100\%       \\
            \hline
            Scratch                    &     &      &      &      &      & 49.0        \\
            \hline
            PointContrast              &     &      & 40.5 & 43.0 & 43.9 & 49.1 (+0.1) \\
            Contrastive Scene Contexts &     &      & 41.6 & 42.9 & 44.6 & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        &     &      & 39.1 & 42.4 & 43.6 & 48.5 (-0.5) \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

@@

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{c | c c c c}
                                       & Scannet & S3DIS & SunRGBD & semanticKITTI \\
            \hline
            Scratch                    & 35.2    &       & 32.0    &               \\
            \hline
            PointContrast              & 36.7    &       & 34.2    &               \\
            Contrastive Scene Contexts & 36.1    &       & 33.2    &               \\
            CME \textbf{(Ours)}        & 37.7    &       & 33.1    &               \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}

>>>>

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{ c | c c c c c c}
                                       & 5\%  & 10\% & 20\%        & 30\%        & 40\%        & 100\%       \\
            \hline
            Scratch                    & 26.9 & 31.1 & 40.7        & 42.2        & 45.7        & 49.0        \\
            \hline
            PointContrast              &      & 35.3 & 40.5 (-0.2) & 43.0 (+0.8) & 43.9 (-1.8) & 49.1 (+0.1) \\
            Contrastive Scene Contexts &      & 35.5 & 41.6 (+0.9) & 42.9 (+0.7) & 44.6 (-1.1) & 49.3 (+0.3) \\
            CME \textbf{(Ours)}        &      & 35.5 & 39.1 (-1.6) & 42.4 (+0.2) & 43.6 (-2.1) & 48.5 (-0.5) \\
        \end{tabular}
    }
    \caption{Scannet Instance Segmentation with Partial Data  (mAP@0.5)}
    \label{table:scannetInstanceVaryingDataAmount}
\end{table*}

@@

\begin{table*}[t!]
    \centering
    \resizebox{0.5\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet & S3DIS & SunRGBD \\
            \hline
            Scratch                    & 35.2    &       & 32.0    \\
            \hline
            PointContrast              & 36.7    &       & 34.2    \\
            Contrastive Scene Contexts & 36.1    &       & 33.2    \\
            CME \textbf{(Ours)}        & 37.7    &       & 33.1    \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table*}
